Finiteness in Cubical Type Theory

### 2020-01-19 figures/finite-classification.tex
down to 16 pages
more

\begin{figure}[h]
  \centering
  \begin{tikzcd}[cramped, row sep=small]
    &
    \ar[ddddd, dash, start anchor={[yshift=4ex]}, end anchor={[yshift=-4ex]}] &
    \text{Ordered} &
    \ar[ddddd, dash, dashed, start anchor={[yshift=4ex]}, end anchor={[yshift=-4ex]}] &
    \text{Unordered}
    \\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \ar[rrrr, dash, start anchor={[xshift=-6ex]}, end anchor={[xshift=10ex]}] &
    &
    &
    &
    {}
    \\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    &
    &
    \text{Split Enumerable}
      \; \ref{split-enumerable}
      \ar[d, xshift=-1ex, bend right=30]
      &
    &
    \\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \text{Discrete} &
    &
    \text{Manifest Bishop}
      \ar[u, xshift=1ex, bend right=30]
      \ar[rr, end anchor=south west, start anchor=south east, bend right=10, crossing over]
      \; \ref{manifest-bishop}
      &
    &
    \text{Cardinal}
      \; \ref{cardinal}
      \ar[ll, start anchor=north west, end anchor=north east, bend right=10, "\text{linOrd}" description]
    \\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \ar[rrrr, dash, dashed, start anchor={[xshift=-6ex]}, end anchor={[xshift=10ex]}] &
    &
    &
    &
    {}
    \\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \text{Non Discrete} &
    {} &
    \text{Manifest Enumerable}
      \; \ref{manifest-enumerability}
      \ar[from=uu, xshift=-1ex, bend right=30, crossing over]
      \ar[uu, bend right=30,  "\text{Discrete}" description]
      \ar[rr, start anchor=south east, end anchor=south west, bend right=10, crossing over]
      &
    {}
    &
    \text{Kuratowski}
      \; \ref{kuratowski}
      \ar[ll, start anchor=north west, end anchor=north east, bend right=10,  "\text{linOrd}" description]
      \ar[uu, xshift=1ex, bend right=30,  "\text{Discrete}" description]
      \ar[from=uu, xshift=-1ex, bend right=30, crossing over]
  \end{tikzcd}
  \caption{Classification of the strong definitions of finiteness, according to
    whether they are discrete (imply decidable equality) and whether they induce
    a linear order.}
  \label{finite-classification}
\end{figure}

>>>>

\begin{figure}
  \centering
  \begin{tikzcd}[cramped, row sep=small]
    &
    \ar[ddddd, dash, start anchor={[yshift=4ex]}, end anchor={[yshift=-4ex]}] &
    \text{Ordered} &
    \ar[ddddd, dash, dashed, start anchor={[yshift=4ex]}, end anchor={[yshift=-4ex]}] &
    \text{Unordered}
    \\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \ar[rrrr, dash, start anchor={[xshift=-6ex]}, end anchor={[xshift=10ex]}] &
    &
    &
    &
    {}
    \\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    &
    &
    \text{Split Enumerable}
      \; \ref{split-enumerable}
      \ar[d, xshift=-1ex, bend right=30]
      &
    &
    \\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \text{Discrete} &
    &
    \text{Manifest Bishop}
      \ar[u, xshift=1ex, bend right=30]
      \ar[rr, end anchor=south west, start anchor=south east, bend right=10, crossing over]
      \; \ref{manifest-bishop}
      &
    &
    \text{Cardinal}
      \; \ref{cardinal}
      \ar[ll, start anchor=north west, end anchor=north east, bend right=10, "\text{linOrd}" description]
    \\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \ar[rrrr, dash, dashed, start anchor={[xshift=-6ex]}, end anchor={[xshift=10ex]}] &
    &
    &
    &
    {}
    \\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \text{Non Discrete} &
    {} &
    \text{Manifest Enumerable}
      \; \ref{manifest-enumerability}
      \ar[from=uu, xshift=-1ex, bend right=30, crossing over]
      \ar[uu, bend right=30,  "\text{Discrete}" description]
      \ar[rr, start anchor=south east, end anchor=south west, bend right=10, crossing over]
      &
    {}
    &
    \text{Kuratowski}
      \; \ref{kuratowski}
      \ar[uu, xshift=1ex, bend right=30,  "\text{Discrete}" description]
      \ar[from=uu, xshift=-1ex, bend right=30, crossing over]
  \end{tikzcd}
  \caption{Classification of finiteness predicates according to whether they are
    discrete (imply decidable equality) and whether they induce a linear order.}
  \label{finite-classification}
\end{figure}%

### 2020-01-19 paper.tex
more

  We formalise our work in Cubical Agda, and we implement a library for proof
  search (including combinators for level-polymorphic fully generic currying),
  and demonstrate how it can be used to both prove properties and synthesise
  full functions given desired properties.
\end{abstract}
\section{Introduction}
\subsection{Foreword}
In constructive mathematics we are often preoccupied with \emph{why} something
is true.
Take finiteness, for example.
There are a handful of ways to demonstrate some type is finite: we could provide
a surjection from another finite type; we could show that any collection of its
elements larger than some bound contains duplicates; or that any stream of its
elements contain duplicates.

@@

The finiteness predicates we are interested in are organised in
Figure~\ref{finite-classification}.
We will explore two aspects of each predicate: its relation with the other
predicates, and its topos-theoretic classification.

When we say ``relation'' we are referring to the arrows in
Figure~\ref{finite-classification}.
The proofs, then, amount to a function which inhabits each arrow.
Each unlabelled arrow is a weakening: i.e., every manifest Bishop finite set
is manifest enumerable.
The labelled arrows are strengthening proofs: i.e. every manifest enumerable set
\emph{with decidable equality} is manifest Bishop finite.

@@

All of our work is formalised in Cubical Agda
\cite{vezzosiCubicalAgdaDependently2019}.
We will make mention of the few occasions where the formalisation of some proof
is of interest, but the main place where we will discuss the code is in the
final section, where we implement a library for proof search, based on
omniscience and exhaustibility.
We also use this section to demonstrate some \emph{computation} using
univalence: our proof search library can deal seamlessly with functions, testing
them for equality, synthesising them, etc.
\subsection{Related Work}
\subsection{Notation}

\section{Finiteness Predicates}
\subsection{Split Enumerable}
\begin{rm-definition}[Split Enumerable Set]
  \begin{equation}
    \mathcal{E}!(A) = \Sigma {(\mathit{xs} : \textbf{List}(A))} , \Pi {(x : A)} , x \in xs
  \end{equation}
  We call the first component of this pair the ``support'' list, and the second
  component the ``cover'' proof.
  This definition is what is referred to as \verb+Listable+ in
  \cite{firsovDependentlyTypedProgramming2015}.
\end{rm-definition}

\section{Relations Between Each Finiteness Definition}
\section{Topos}
\section{Countably Infinite Types}
\section{Search}

@@

%   Any cardinal finite type with a (decidable) total order is manifestly Bishop
%   finite.
%   This proof is quite involved, and will rely on several subsequent lemmas, so
%   we will give only its outline here.
%   \begin{itemize}
%     \item First, we will convert to manifest enumerability: knowing that the
%       underlying type is discrete (theorem~\ref{cardinal-finite-discrete}) we can
%       go from manifest enumerability to split enumerability
%       (lemma~\ref{manifest-enum-to-split}), and subsequently to manifest Bishop
%       finiteness (lemma~\ref{split-enum-to-manifest-bishop}).
%     \item To convert to manifest enumerability, we need to provide a support
%       list: this cannot simply be the support list hidden under the truncation,
%       since that would violate the hiding promised by the truncation.
%       Instead, we sort the list (using insertion sort).
%       We must, therefore, prove that insertion sort is invariant under all
%       support lists in cardinal finiteness proofs.
%     \item We do this by first showing that all support lists in cardinal
%       finiteness proofs are permutations of each other, and then that insertion
%       sort is invariant under permutations.
%     \item Given our particular definition of permutations, cover proofs
%       transfers naturally between lists which are permutations of each other.
%   \end{itemize} 
% Now we will build up the toolkit we need to perform the above steps.
% First, permutations.
% \begin{rm-definition}[List Permutations]
%   We say that two lists are permutations of each other if there is an
%   isomorphism between membership proofs
%   \cite{danielssonBagEquivalenceProofRelevant2012}.
%     \mathit{xs} \leftrightsquigarrow \mathit{ys} = \Pi {(x : A)} , x \in \mathit{xs} \iff x \in \mathit{ys}
% \end{rm-definition}
%   Insertion sort is invariant under permutations.
%     \mathit{xs} \leftrightsquigarrow \mathit{ys} \implies \text{sort}(\mathit{xs}) \equiv \text{sort}(\mathit{ys})
%   First, we prove two properties about insertion sort:
%   \begin{enumerate}
%     \item It returns a sorted list.
%     \item It a returns a list that is a permutation of its input.
%   \end{enumerate}
%   The second of these points allows us to show that \(\text{sort}(\mathit{xs})\)
%   is a permutation of \(\text{sort}(\mathit{ys})\).
%     \text{sort}(\mathit{xs}) \leftrightsquigarrow \mathit{xs} \leftrightsquigarrow \mathit{ys} \leftrightsquigarrow \text{sort}(\mathit{ys})
%   Then, we show that any lists which are both sorted and permutations of each
%   other are equal.
%   Both of these conditions are true for the output of \(\text{sort}\).
% \section{Kuratowski Finiteness} \label{kuratowski}
% Finally we arrive at Kuratowski finiteness
% \cite{kuratowskiNotionEnsembleFini1920}.
% \begin{rm-definition}[Kuratowski-Finite Set]
%   The Kuratowski finite set is a free join semilattice (or, equivalently, a free
%   commutative idempotent monoid).
%   HITs are required to define this type
%   \cite{altenkirchDefinableQuotientsType2011}:
%     \begin{aligned}
%       \mathcal{K}(A) =&
%        \; \cdot \dblcolon \cdot : A \times \mathcal{K}(A) \rightarrow \mathcal{K}(A) ; \\
%       \vert& \; [] : \mathcal{K}(A) ; \\
%       \vert& \; \text{com} : \Pi (x, y: A) , \Pi (\mathit{xs}: \mathcal{K}(A)) , x \dblcolon y \dblcolon \mathit{xs} \equiv y \dblcolon x \dblcolon \mathit{xs} ; \\
%       \vert& \; \text{dup} : \Pi (\mathit{x}: A) , \Pi (\mathit{xs}: \mathcal{K}(A)) , x \dblcolon x \dblcolon \mathit{xs} \equiv x \dblcolon \mathit{xs} ; \\
%       \vert& \; \text{trunc} : \Pi (\mathit{xs}, \mathit{ys}: \mathcal{K}(A)) , \Pi (p, q : \mathit{xs} \equiv \mathit{ys}) , p \equiv q ;
%     \end{aligned}
%   The \(\text{com}\) and \(\text{dup}\) constructors effectively add
%   commutativity and idempotency to the free monoid (the list), which is made by
%   the first two constructors.
%   The last constructor makes \(\mathcal{K}(A)\) a set.

%   To eliminate from \(\mathcal{K}(A)\), we have to provide equations for each of
%   the point constructors which obey the equations of the path constructors.
%   For \(\text{com}\) and \(\text{dup}\), this means ensuring that the fold is
%   commutative and idempotent, whereas \(\text{trunc}\) means we can only
%   eliminate into sets.
% \end{rm-definition}

% Other representations of \(\mathcal{K}\) \cite{fruminFiniteSetsHomotopy2018}
% are more explicit constructions of the free join semilattice (i.e. there is a
% point constructors for union instead of cons, and then path constructors for
% the associativity and identity laws), but we have found this representation
% easier to work with.
% Nonetheless, the alternative representation is included in our formalisation,
% and proven equivalent to the representation here.
% \begin{rm-definition}[Membership of \mathcal{K}]
%   First, we need to provide equations for the two point constructors.
%   \(x \in [] = \bot\), and \(x \in y \dblcolon \mathit{xs} = \lVert (x \equiv y)
%   + (x \in \mathit{xs}) \rVert \).
%   The \(\text{com}\) and \(\text{dup}\) constructors are handled by proving that
%   the truncated form of \(+\) is itself commutative and idempotent.
%   The type of propositions is itself a set, satisfying the \(\text{trunc}\)
%   constructor.
% \end{rm-definition}
% \begin{rm-definition}[Kuratowski Finiteness]
%   A type is Kuratowski finite iff there exists a Kuratowski Set which contains
%   all of its elements.
%   \begin{equation}
%     \mathcal{K}^{f}(A) = \Sigma {(\mathit{xs} : \mathcal{K}(A))} , \Pi (x : A) , x \in \mathit{xs}
%   \end{equation}
% \end{rm-definition}

@@

% \cite{fruminFiniteSetsHomotopy2018} explores many of the same notions as we do
% here: cardinal finiteness, and Kuratowski finite sets.
% Our work makes extensive use of the computational properties of CuTT, however,
% and we are able to formalise the finiteness of function objects.
\bibliographystyle{splncs04}
\bibliography{bibliography.bib}
\end{document}

>>>>

  We formalise our work in Cubical Agda, and we implement a library for proof
  search (including combinators for level-polymorphic fully generic currying),
  and demonstrate how it can be used to both prove properties and synthesise
  full functions given desired properties.
  \keywords{Agda \and Homotopy Type Theory \and Cubical Type Theory \and
    Dependent Types \and Finiteness \and Topos \and Kuratowski finite}
\end{abstract}

\section{Introduction}
\subsection{Foreword}
In constructive mathematics we are often preoccupied with \emph{why} something
is true.
Take finiteness, for example.
There are a handful of ways to demonstrate some type is finite: we could provide
a surjection from another finite type; we could show that any collection of its
elements larger than some bound contains duplicates; or that any stream of its
elements contain duplicates.

@@

The finiteness predicates we are interested in are organised in
Figure~\ref{finite-classification}.
We will explore two aspects of each predicate: its relation to the other
predicates, and its topos-theoretic classification.

When we say ``relation'' we are referring to the arrows in
Figure~\ref{finite-classification}.
The proofs, then, amount to a function which inhabits each arrow.
Each unlabelled arrow is a weakening: i.e., every manifest Bishop finite set
is manifest enumerable.
The labelled arrows are strengthening proofs: i.e., every manifest enumerable set
\emph{with decidable equality} is manifest Bishop finite.

@@

All of our work is formalised in Cubical Agda
\cite{vezzosiCubicalAgdaDependently2019}.
We will make mention of the few occasions where the formalisation of some proof
is of interest, but the main place where we will discuss the code is in the
final section, where we implement a library for proof search, based on
omniscience and exhaustibility.
We also use this section to demonstrate some \emph{computation} using
univalence: our proof search library can deal seamlessly with functions, testing
them for equality, synthesising them, etc.
\subsection{Related Work}
\subsection{Notation}
\todo[inline]{Basic MLTT Notation: \(\Pi\), \(\Sigma\), etc}
\todo[inline]{Paths, Univalence, isomorphisms}
\todo[inline]{HITs}

\section{Finiteness Predicates}
\subsection{Kuratowski Finiteness}
\begin{rm-definition}[Kuratowski Finite Subset]
  \(\mathcal{K}(A)\) is the type of Kuratowski-finite subsets of \(A\).
  \begin{equation}
    \begin{aligned}
      \mathcal{K}(A) =&
             \; \eta : A \rightarrow \mathcal{K}(A) ; \\
      \vert& \; \emptyset : \mathcal{K}(A) ; \\
      \vert& \; \wc \cup \wc : \mathcal{K}(A) \rightarrow \mathcal{K}(A) \rightarrow \mathcal{K}(A) ; \\
      \vert& \; \text{associative} : \Pi (\mathit{xs}, \mathit{ys}, \mathit{zs}: \mathcal{K}(A)) , (\mathit{xs} \cup \mathit{ys}) \cup \mathit{zs} \equiv \mathit{xs} \cup (\mathit{ys} \cup \mathit{zs}) ; \\
      \vert& \; \text{identity} : \Pi (\mathit{xs}: \mathcal{K}(A)) , \emptyset \cup \mathit{xs} \equiv \mathit{xs} ; \\
      \vert& \; \text{commutative} : \Pi (\mathit{xs}, \mathit{ys}: \mathcal{K}(A)) , \mathit{xs} \cup \mathit{ys} \equiv \mathit{ys} \cup \mathit{xs} ; \\
      \vert& \; \text{idempotent} : \Pi (\mathit{xs}: \mathcal{K}(A)) , \mathit{xs} \cup \mathit{xs} \equiv \mathit{xs} ; \\
      \vert& \; \text{trunc} : \Pi (\mathit{xs}, \mathit{ys}: \mathcal{K}(A)) , \Pi (p, q : \mathit{xs} \equiv \mathit{ys}) , p \equiv q ;
    \end{aligned}
  \end{equation}
\end{rm-definition}
The Kuratowski finite subset is a free join semilattice (or, equivalently, a
free commutative idempotent monoid).
Though it would be possible to use this type as-is, we found it easier to work
with the following type as it has fewer path constructors.
\begin{equation}
  \begin{aligned}
    \mathcal{K}(A) =&
           \; [] : \mathcal{K}(A) ; \\
    \vert& \; \wc \dblcolon \wc : A \rightarrow \mathcal{K}(A) \rightarrow \mathcal{K}(A) ; \\
    \vert& \; \text{com} : \Pi (x, y: A) , \Pi (\mathit{xs} : \mathcal{K}(A)) , x \dblcolon y \dblcolon \mathit{xs} \equiv y \dblcolon x \dblcolon \mathit{xs} ; \\
    \vert& \; \text{dup} : \Pi (x : A) , \Pi (\mathit{xs} : \mathcal{K}(A)) , x \dblcolon x \dblcolon \mathit{xs} \equiv x \dblcolon \mathit{xs} ; \\
    \vert& \; \text{trunc} : \Pi (\mathit{xs}, \mathit{ys}: \mathcal{K}(A)) , \Pi (p, q : \mathit{xs} \equiv \mathit{ys}) , p \equiv q ;
  \end{aligned}
\end{equation}
What we've done here is basically pulled out the ``monoid'' part of ``free
commutative idempotent monoid'': the first two constructors now construct a
list, which is a representation of the free monoid \emph{without} quotient
types.
This obviates the need for the associative and identity constructors.
We have proven both types equivalent in our formalisation.

Next, we need a way to say that a type is Kuratowski finite, rather than just
some subset.
For that, we will need to define membership of \(\mathcal{K}\).
\begin{rm-definition}[Membership of \mathcal{K}]
  First, we need to provide equations for the two point constructors.
  \(x \in [] = \bot\), and \(x \in y \dblcolon \mathit{xs} = \lVert (x \equiv y)
  + (x \in \mathit{xs}) \rVert \).
  The \(\text{com}\) and \(\text{dup}\) constructors are handled by proving that
  the truncated form of \(+\) is itself commutative and idempotent.
  The type of propositions is itself a set, satisfying the \(\text{trunc}\)
  constructor.
\end{rm-definition}
\begin{rm-definition}[Kuratowski Finiteness]
  A type is Kuratowski finite iff there exists a Kuratowski finite subset which
  contains all of its elements.
  \begin{equation}
    \mathcal{K}^{f}(A) = \Sigma {(\mathit{xs} : \mathcal{K}(A))} , \Pi (x : A) , x \in \mathit{xs}
  \end{equation}
\end{rm-definition}

\subsection{Split Enumerable}
\begin{rm-definition}[Split Enumerable Set]
  \begin{equation}
    \mathcal{E}!(A) = \Sigma {(\mathit{xs} : \textbf{List}(A))} , \Pi {(x : A)} , x \in xs
  \end{equation}
  We call the first component of this pair the ``support'' list, and the second
  component the ``cover'' proof.
\end{rm-definition}
In this, and the rest of the definitions in the paper, we tend to prefer
list-based notions of finiteness.
This is purely a matter of perspective, however: the definition above is
precisely equivalent to a split surjection from a finite prefix of the natural
numbers.
\begin{rm-lemma}
  \begin{equation}
    \mathcal{E}!(A) \simeq \Sigma (n : \mathbb{N}) , \left( \mathbf{Fin}(n) \twoheadrightarrow ! \; A \right)
  \end{equation}
\end{rm-lemma}
We have proven this statement in our formalisation, but it is worth pointing out
that the proof is nearly trivial: after inlining the definitions of
\(\mathbf{List}\), \(\in\), and \(\twoheadrightarrow!\), it becomes clear that
the two terms are basically the same anyway, modulo the reassociation of
\(\Sigma\).

Split enumerability is quite a strong predicate, implying both decidable
equality and a total order on the underlying type.
This

\subsection{Manifest Bishop}
\subsection{Manifest Enumerable}
\subsection{Cardinal}
\section{Relations Between Each Finiteness Definition}
\section{Topos}
\section{Countably Infinite Types}
\section{Search}

@@

% \begin{rm-theorem}
%   Any cardinal finite type with a (decidable) total order is manifestly Bishop
%   finite.
% \end{rm-theorem}
% \begin{proof}
%   This proof is quite involved, and will rely on several subsequent lemmas, so
%   we will give only its outline here.
%   \begin{itemize}
%     \item First, we will convert to manifest enumerability: knowing that the
%       underlying type is discrete (theorem~\ref{cardinal-finite-discrete}) we can
%       go from manifest enumerability to split enumerability
%       (lemma~\ref{manifest-enum-to-split}), and subsequently to manifest Bishop
%       finiteness (lemma~\ref{split-enum-to-manifest-bishop}).
%     \item To convert to manifest enumerability, we need to provide a support
%       list: this cannot simply be the support list hidden under the truncation,
%       since that would violate the hiding promised by the truncation.
%       Instead, we sort the list (using insertion sort).
%       We must, therefore, prove that insertion sort is invariant under all
%       support lists in cardinal finiteness proofs.
%     \item We do this by first showing that all support lists in cardinal
%       finiteness proofs are permutations of each other, and then that insertion
%       sort is invariant under permutations.
%     \item Given our particular definition of permutations, cover proofs
%       transfers naturally between lists which are permutations of each other.
%   \end{itemize} 
% \end{proof}
% Now we will build up the toolkit we need to perform the above steps.
% First, permutations.
% \begin{rm-definition}[List Permutations]
%   We say that two lists are permutations of each other if there is an
%   isomorphism between membership proofs
%   \cite{danielssonBagEquivalenceProofRelevant2012}.
%   \begin{equation}
%     \mathit{xs} \leftrightsquigarrow \mathit{ys} = \Pi {(x : A)} , x \in \mathit{xs} \iff x \in \mathit{ys}
%   \end{equation}
% \end{rm-definition}
% \begin{rm-lemma}
%   Insertion sort is invariant under permutations.
%   \begin{equation}
%     \mathit{xs} \leftrightsquigarrow \mathit{ys} \implies \text{sort}(\mathit{xs}) \equiv \text{sort}(\mathit{ys})
%   \end{equation}
% \end{rm-lemma}
% \begin{proof}
%   First, we prove two properties about insertion sort:
%   \begin{enumerate}
%     \item It returns a sorted list.
%     \item It a returns a list that is a permutation of its input.
%   \end{enumerate}
%   The second of these points allows us to show that \(\text{sort}(\mathit{xs})\)
%   is a permutation of \(\text{sort}(\mathit{ys})\).
%   \begin{equation}
%     \text{sort}(\mathit{xs}) \leftrightsquigarrow \mathit{xs} \leftrightsquigarrow \mathit{ys} \leftrightsquigarrow \text{sort}(\mathit{ys})
%   \end{equation}
%   Then, we show that any lists which are both sorted and permutations of each
%   other are equal.
%   Both of these conditions are true for the output of \(\text{sort}\).
% \end{proof}
% \section{Kuratowski Finiteness} \label{kuratowski}
% Finally we arrive at Kuratowski finiteness
% \cite{kuratowskiNotionEnsembleFini1920}.

% Other representations of \(\mathcal{K}\) \cite{fruminFiniteSetsHomotopy2018}
% are more explicit constructions of the free join semilattice (i.e. there is a
% point constructors for union instead of cons, and then path constructors for
% the associativity and identity laws), but we have found this representation
% easier to work with.
% Nonetheless, the alternative representation is included in our formalisation,
% and proven equivalent to the representation here.

@@

% \cite{fruminFiniteSetsHomotopy2018} explores many of the same notions as we do
% here: cardinal finiteness, and Kuratowski finite sets.
% Our work makes extensive use of the computational properties of CuTT, however,
% and we are able to formalise the finiteness of function objects.

\todo[inline]{Add funding ack:

  This work has been supported by the Science Foundation Ireland under the
  following grant: 13/RC/2D94 to Irish Software Research Centre.
}
\bibliographystyle{splncs04}
\bibliography{bibliography.bib}
\end{document}
